Analyzing State-Level Respondent Estimates Using Ratio Estimators: A Case Study with 2022 ACS Data

### 2024-11-22 paper/paper.qmd
Update LLM usage and readme
Update Abstract

---
title: "Analyzing State-Level Respondent Estimates Using Ratio Estimators: A Case Study with 2022 ACS Data"
author: 
  - Yunkai Gu, Anqi Xu, Yitong Wang
thanks: "Code and data are available at: https://github.com/Anjojoo/State-Level-Respondent-Estimates."
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
toc: true
---

@@

data <- read.csv(file = here::here("data/02-analysis_data/analysis_data.csv"))

@@

doctoral_data %>%
  kable(format = "simple", col.names = c('STATEICP', 'doctoral_count'))
```

@@

estimated_data %>% select(-doctoral_count) %>%
  kable(format = "simple", col.names = c('STATEICP',  'estimated_total_respondents'))
```

@@

state_counts %>% select(-doctoral_count) %>%
  kable(format = "simple", col.names = c('STATEICP', 'estimated_total_respondents', 'total_count_respondents', 'difference'))
```

>>>>

---
title: "Analyzing State-Level Respondent Estimates Using Ratio Estimators: A Case Study with 2022 ACS Data"
author: 
  - Yunkai Gu, Anqi Xu, Yitong Wang
thanks: "Code and data are available at: https://github.com/Anjojoo/State-Level-Respondent-Estimates."
date: today
date-format: long
abstract: "This study analyzes state-level respondent estimates using data from the 2022 American Community Survey (ACS) accessed via IPUMS, and focuses on individuals with doctoral degrees and employs the ratio estimator approach to predict total respondents in each state, using California as a reference point. The results reveal discrepancies between estimates and actual figures, highlighting the limitations of assuming uniform ratios across states. These differences are attributed to variations in demographics, educational policies, and economic conditions. The analysis underscores the utility of statistical methods like ratio estimators for scalable estimates while emphasizing the importance of accounting for regional variations in such analyses."
format: pdf
number-sections: true
toc: true
---

@@

data <- read.csv(file = here::here("data/01-analysis_data/analysis_data.csv"))

@@

doctoral_data %>%
  kable(format = "simple", col.names = c('State', 'Doctoral Counts'))
```

@@

estimated_data %>% select(-doctoral_count) %>%
  kable(format = "simple", col.names = c('State',  'Estimated Respondents'))
```

@@

state_counts %>% select(-doctoral_count) %>%
  kable(format = "simple", col.names = c('State', "Estimated Respondents", 
                                         "Actual Respondents", "Difference"))
```
